---
title: "Data607 week 9 Assignment Zainab"
author: "Zainab.O"
date: "2023-10-27"
output: html_document
---
Assignment Description - Web APIs
The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis. You’ll need to start by signing up for an API key. Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.

1) Signup for an account on nytimes site to get a API key
2) I select Article Read API
3) I want to see want the records say on birth rates or infertility 

FIRST : LOAD LIBRAIAES

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


LIBRARIES
```{r}
library(httr)
library(rjson)
library(jsonlite)
library(dplyr)
library(tidyverse)
```

GET ACESS TO NYT ARTICLES

```{r}
key = 'NuD0CCleGeVby1y8vQRqCd8AyUSkIj0B'
key
```

```{r}
nyt_link = GET("https://api.nytimes.com/svc/search/v2/articlesearch.json?q=birth_rate&api-key=NuD0CCleGeVby1y8vQRqCd8AyUSkIj0B")
nyt_link
```
```{r}
http_error(nyt_link)
```

```{r}
head(nyt_link)
```
```{r}
summary(nyt_link)
```
```{r}
#nyt_linksv2
```


#Content is a httr fucntion used to extract content from a request, here speifically I am extracting text(strings/characters). I used "as"  to be speific to what I want.The reason why is beacuse when I brefly veiwed the file suing head I got a lot of numbers but did not know what they are associated with
```{r}
nyt_linksv2= content(nyt_link, as = "text")
```
#Now I am attempting to put it in a dataframe and hopefully is comes out readable. 
#1) use the fucntion JSON to read content in JSON format and convert into a strong into an Robject
#2)as.data.frame converts an object into a data frame
```{r}
nyt_linkdf = nyt_linksv2 %>%
  fromJSON() %>%
  as.data.frame()
```

```{r}
colnames(nyt_linkdf)
```
```{r}
head(nyt_linkdf)
```
I have made a dataframe and it needs to be cleaned up

I am going to RENAME my colmuns

```{r}
colnames(nyt_linkdf) = c("status","copyright","abstract","web_url","snippet","lead_paragraph","print_section","print_page","source", "multimedia","headline","keywords", "pub_date","document_type", "news_desk","section_name", "docs.byline" ,"type_of_material", "id","word_count","uri","meta.hits","meta.offset" , "meta.time" )
```

```{r}
nyt_linkdf
```
```{r}
nyt_linkdf2 = nyt_linkdf[,c(-1)]
nyt_linkdf
```

```{r}
nyt_linkdf2= nyt_linkdf %>%
  select(-c("lead_paragraph"))
nyt_linkdf2
```
```{r}
nyt_linkdf2= nyt_linkdf %>%
  select(-c("print_section","docs.byline","headline","lead_paragraph","multimedia","news_desk","section_name"))
nyt_linkdf2
```

The Goas was to read in a Json file from New York Times api into Rstudio and create a R data frame. I made data frame on birth rates. I cleaned it up by eliminated columns I felt were not needed. I have 10 rows , so 10 articles on birth rates (or were ID by by the query ).

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
